Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-18 Ch1_movement_rates/Ch1_Figures.Rmd
Editing kernel density estimations for parameter values from weibull dists.
Updating figure for dispersaal and dispersion

```{r}
disp_df %>%
  group_by(., model) %>%
  sample_n(., 5000) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersion

disp_df %>%
  group_by(., model) %>%
  sample_n(., 5000) %>%
  ggplot(., aes(y = av.disp, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Average dispersal", y = "Dispersal in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersal

@@

@@

## Variation 1 - violin plot with 200 out of 1000 of the parameter fits

@@

# ggsave2(filename = "Ch1_movement_rates/Figures/weib_plot.png")

>>>>

```{r}
disp_df %>%
  group_by(., model) %>%
  #sample_n(., 5000) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersion

disp_df %>%
  group_by(., model) %>%
  #sample_n(., 5000) %>%
  ggplot(., aes(y = av.disp, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Average dispersal", y = "Dispersal in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersal

@@

# Idea for dispersal and dispersion
Too many points, since we have 500k seeds, take 2%

```{r fig.height=12}

points_plot <- function(seed.data, s.size = 1000, xylims=1250, lalpha = 0.3){
  seed.data %>% 
    drop_na(s.id) %>% 
    mutate(ov500 = ifelse(disp <500, "non", "ldd")) %>% 
    sample_n(s.size) %>% 
      ggplot(., aes(x = xloc, y = yloc, color = ov500)) +
      geom_point(alpha = lalpha) +
      coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
      theme_bw()

}

A <- points_plot(seed.data = cp.df)
B <- points_plot(seed.data = pp.df)
C <- points_plot(seed.data = np.df)

plot_grid(A, B, C, nrow = 3)

# To do:
# Remove xy labels
# change colors so only over 500 shows blue
# remove legends
# Add boxplots for dispersion next to it
# Am I adding dispersal?
# For final figure increase sample size to 50,000 so we have 10% of the data visualized.

@@

@@

#ggsave2(filename = "Ch1_movement_rates/Figures/Figure5.png")

```{r}
library(kde1d)

# Kernel density estimation:

cp.shape.kde <- kde1d(weib.boot.cp$est.shape)
pp.shape.kde <- kde1d(weib.boot.pp$est.shape)
np.shape.kde <- kde1d(weib.boot.np$est.shape)

cp.scale.kde <- kde1d(weib.boot.cp$est.scale)
pp.scale.kde <- kde1d(weib.boot.pp$est.scale)
np.scale.kde <- kde1d(weib.boot.np$est.scale)

CIs.cp.shape <- qkde1d(p=c(0.025,0.5, 0.975), cp.shape.kde)
CIs.pp.shape <- qkde1d(p=c(0.025,0.5, 0.975), pp.shape.kde)
CIs.np.shape <- qkde1d(p=c(0.025,0.5, 0.975), np.shape.kde)

CIs.cp.scale <- qkde1d(p=c(0.025,0.5, 0.975), cp.scale.kde)
CIs.pp.scale <- qkde1d(p=c(0.025,0.5, 0.975), pp.scale.kde)
CIs.np.scale <- qkde1d(p=c(0.025,0.5, 0.975), np.scale.kde)

# The proportion of shape parameter values above the sampling distribution is 
prop.above1.10.cp.shape <- 1-pkde1d(q=1.10, cp.shape.kde)
prop.above1.10.pp.shape <- 1-pkde1d(q=1.10, pp.shape.kde)
prop.above1.10.np.shape <- 1-pkde1d(q=1.10, np.shape.kde)

plot(cp.shape.kde$grid_points, cp.shape.kde$values, type="l", lwd=2, bty="l", col="red", ylim = c(0,4))
lines(pp.shape.kde$grid_points, pp.shape.kde$values, col="blue")
lines(np.shape.kde$grid_points, np.shape.kde$values, col="black")

plot(cp.scale.kde$grid_points, cp.scale.kde$values, type="l", lwd=2, bty="l", col="red", ylim = c(0,0.04))
lines(pp.scale.kde$grid_points, pp.scale.kde$values, col="blue")
lines(np.scale.kde$grid_points, np.scale.kde$values, col="black")
